\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-03 paper/sp.tex
optimization

% To-do items
% -----------
% - draft discussion
% - make sure we address the sensibleness and generality of the linear model for the photometric space
% - address the non-convexity of the model (see twitter convo with @andy_l_jones). Plus optimization issues.
% - Coryn's point that we should carefully explain how our model is geometric.
% - related: HWR's point that this is standardizeable candles, like the Ia SNe results.
% - related: Put in an explanation of WHY this works so well.
% - related: Put in an explanation of how it is that we aren't really modeling luminosity or distance but really just generating parallaxes.
% - does the model need a cute name, like The Swan?
% - we need a Facilities list / tags
% - we need a Software list / tags
% - check with WISE experts that we have the correct WISE photometry

@@

@@

We optimize two models, one for Training Set A and one for Training Set B.
For optimization, we use \code{scipy.optimize} \acronym{L-BFGS-B}, starting at
an uninformed starting point in the $\theta$ space.
The optimization is of the objective function given in \equationname~(\ref{eq:objective}) above,
and although this optimization is not convex, it appears to converge to the
same good solution quickly and reliably from multiple different starting points.

The two models are applied to the two splits of the Parent Sample, Parent Sample
A and Parent Sample B, using the A-trained model on Parent Sample B and
\foreign{vice versa}.
For the purposes of assessing the accuracy and precision of the model, this
train-and-test framework constitutes a two-fold cross-validation.
Results of this cross-validation is shown in HOGG WHAT FIGURE.
For the stars with highest \gaia-measured parallax signal-to-noise,
the spectrophotometric model is predicting the \gaia\ parallaxes with little bias
and a scatter of better than 9~percent.

>>>>

% To-do items
% -----------
% - draft discussion
% - make sure we address the sensibleness and generality of the linear model for the photometric space
% - Coryn's point that we should carefully explain how our model is geometric.
% - related: HWR's point that this is standardizeable candles, like the Ia SNe results.
% - related: Put in an explanation of WHY this works so well.
% - related: Put in an explanation of how it is that we aren't really modeling luminosity or distance but really just generating parallaxes.
% - does the model need a cute name, like The Swan?
% - we need a Facilities list / tags
% - we need a Software list / tags
% - check with WISE experts that we have the correct WISE photometry

@@

This optimization is not convex---there are multiple optima in general.
In particular, there is a large, degenerate, pathological optimum where
the exponential function underflows, all parallaxes are predicted to vanish,
and there is no gradient of anything with respect to the parameter $D$-vector $\theta$.
This large, bad optimum (it is a local, not global, optimum) must be avoided in optimization.
In practice we avoid it by optimizing first for the very highest signal-to-noise
(in astrometric parallax) Training Set stars, and then use that first optimum as a
good first guess or initialization for the full optimization.
This method works because in the limit of high signal-to-noise, the problem asymptotically approaches
the convex problem of L1-regularized linear least-square fitting.
Optimization is performed with \code{scipy.optimize} \acronym{L-BFGS-B}.

@@

We optimize two models, one for Training Set A and one for Training Set B.
The two models are applied to the two splits of the Parent Sample, Parent Sample
A and Parent Sample B, using the A-trained model on Parent Sample B and
\foreign{vice versa}.
For the purposes of assessing the accuracy and precision of the model, this
train-and-test framework constitutes a two-fold cross-validation.
Results of this cross-validation is shown in HOGG WHAT FIGURE.
For the stars with highest \gaia-measured parallax signal-to-noise,
the spectrophotometric model is predicting the \gaia\ parallaxes with little bias
and a scatter of better than 9~percent.
